Standardization of ceramic shape: A case study of Iron Age pottery from northeastern Taiwan

### 2023-09-04 analysis/paper/paper.Rmd
checking text labels - they are correct

ggplot(pc_plot,
       aes(phase,
           pc)) +
  geom_violin() + 
  ggforce::geom_sina() +
  xlab("") +
  facet_wrap(~ pcn, ncol = 1) +
  geom_text(data = cv_pcs_all,
            mapping = aes(x = c(2.1, 1.1, 3.1, 2.1, 1.1, 3.1, 2.1, 1.1, 3.1), 
                          y = 8.5, 
                          label = cv_label),
            size = 2,
            color= "red",
            hjust = -0.1,
            vjust= -1)+
  theme_minimal()

>>>>

ggplot(pc_plot,
       aes(phase,
           pc)) +
  geom_violin() + 
  ggforce::geom_sina() +
  xlab("") +
  facet_wrap(~ pcn, ncol = 1) +
  geom_text(data = cv_pcs_all,
            mapping = aes(x = c(2.1,   # upper middle 
                                1.1,   # upper left
                                3.1,   # upper right
                                2.1,   # middle middle
                                1.1,   # middle left
                                3.1,   # middle right
                                2.1,   # lower middle
                                1.1,   # lower left
                                3.1),  # lower right
                          y = 8.5, 
                          label = cv_label),
            size = 2,
            color= "red",
            hjust = -0.1,
            vjust= -1)+
  theme_minimal()
